{\fontfamily{ptm}\selectfont Linear Convergence of Stochastic Nesterov's Accelerated Proximal Gradient method under Interpolation Hypothesis, Truth or Just a Dream?}

### 2025-07-22 Notebook LaTEX/SAGD Under Interpolation/main.tex
>w<, changes

@@

        Conditional expectation wrt to a random variable is not directly defined, it's instead only defined with respect to some Sigma algebra. 

>>>>

        Remark the following definitions
        \begin{definition}[conditional expectations]
            Given probability space $(\Omega, \mathcal F_0, \prob)$ and, $\mathcal F \subseteq \mathcal F_0$, and a random variable $X \in \mathcal F$ such that $\expect |X| < \infty$. 
            We define the conditional expectation of $X$ given $\mathcal F$, $\expect [X| \mathcal F]$ to be any random variable $Y$ that has 
                \item $Y \in \mathcal F$, i.e: $Y$ is $\mathcal F$ measurable. 
                \item For all $A \in \mathcal F$, $\int_A X d\prob = \int_A Y d\prob$. 
            \todoinline{CITATIONS HERE NEEDED. }
        The conditional expectation exists and it's unique. 

@@

        Conditional expectation wrt to a random variable is not directly defined, it's instead only defined with respect to some sigma algebra. 
        The conditional expectation exists, and it's unique. 
